Procedural Terrain \\ {\large Final project for class CS6491 Computer Graphics}

### 2015-11-29 Paper/Paper.tex
small improvements of the paper

In our implementation, the biomes are initialized with the temperature and moisture information from the previous step. The user can then paint the different biomes directly on the terrain to fine-tune the biome assignment.

The terrain is then rendered using different textures for each biome (Fig. \ref{fig:terrainBiomes}). Furthermore, the biomes specify if and what grass is used and what trees are planted.
\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{images/TerrainBiomes1}
		\caption{biomes are painted on the terrain}
		\label{fig:terrainBiomes1}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{images/TerrainBiomes2}
		\caption{textured terrain based on the biomes}
		\label{fig:terrainBiomes2}
	\end{subfigure}
	\caption{Assigning biomes to the terrain}\label{fig:terrainBiomes}
\end{figure*}

\subsection{Grass}
\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{images/Grass2}
		\caption{transparent quads forming the grass blades}
		\label{fig:grass1}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{images/Grass1}
		\caption{adding a texture leads to the final appearance}
		\label{fig:grass2}
	\end{subfigure}
	\caption{Grass}\label{fig:grass}
\end{figure*}
For rendering grass, we are using the concepts presented in \cite{KurtPelzer.}. An implementation of it comes with the 3d engine we are using, the jMonkeyEngine\footnote{\url{http://jmonkeyengine.org/}}.
A blade of grass is displayed using two transparent quads that are orthogonal to each other (Fig. \ref{fig:grass1}). The shades are then randomly placed on the terrain, the density distribution varies with the biomes. Finally, a texture is applied to complete the grass rendering (Fig. \ref{fig:grass2}).

>>>>

In our implementation, the biomes are initialized with the temperature and moisture information from the previous steps. The user can then paint the different biomes directly on the terrain to fine-tune the biome assignment.

The terrain can be rendered using different textures for each biome (Fig. \ref{fig:terrainBiomes}). Furthermore, the biomes specify if and what grass is used and what trees are planted.
\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{images/TerrainBiomes1}
		\caption{biomes are painted on the terrain}
		\label{fig:terrainBiomes1}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{images/TerrainBiomes2}
		\caption{textured terrain based on the biomes}
		\label{fig:terrainBiomes2}
	\end{subfigure}
	\caption{Assigning biomes to the terrain}\label{fig:terrainBiomes}
\end{figure*}

\subsection{Grass}
\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{images/Grass2}
		\caption{transparent quads forming the grass blades}
		\label{fig:grass1}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{images/Grass1}
		\caption{adding a texture leads to the final appearance}
		\label{fig:grass2}
	\end{subfigure}
	\caption{Grass}\label{fig:grass}
\end{figure*}
For rendering grass, we use the concepts presented in \cite{KurtPelzer.}. An implementation of it comes with the 3d engine we are using, the jMonkeyEngine\footnote{\url{http://jmonkeyengine.org/}}.
A blade of grass is displayed using two transparent quads that are orthogonal to each other (Fig. \ref{fig:grass1}). The shades are then randomly placed on the terrain, the density distribution varies with the biomes. Finally, a texture is applied to complete the grass rendering (Fig. \ref{fig:grass2}).
